Supplemental Materials

### 2021-07-12 supplement/supplement-main.Rmd
supplement fixes

fit_s2_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s2_reg,
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 46179,
  file = "../local/fit_s2_vaccIntent.rds"
)

@@

  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption, escape = T, format = "latex") %>% 
    kableExtra::kable_classic(full_width=F)
}

fit_s2_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(diseaseRisk|post)","", Term)
    )
  ) %>% 
  make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")

@@

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  # group_by(scale) %>% 
  # mutate(post = post/sd(post), pre = pre/sd(pre)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

fit_s3_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions combining data from Experiments 3a and 3b.")
```

@@

fit_s3a_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="A"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 69568,
  file = "../local/fit_s3a_vaccIntent.rds"
)

fit_s3b_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="B"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 69568,
  file = "../local/fit_s3b_vaccIntent.rds"
)

fit_s3a_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3a.")

fit_s3b_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3b.")
```

@@

```{r echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the toxins intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.15),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

fit_s4_vaccIntent <- brm(
  response ~ phase*vacc_news + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s4_reg %>% filter(scale=="vaccIntent"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 40725,
  file = "../local/fit_s4_vaccIntent.rds"
)

fit_s4_vaccIntent %>% 
make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|posttest)","", Term)
    ),
    Term = gsub("vacc_news", "awareness", Term)
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
```

@@

```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4. Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York. Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak. In both plots, error bars represent 95\\% confidence intervals."}
s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(posttest = rescale_beta(posttest, -3, 3), pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll95, ymax=ul95, color=vacc_news, shape=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2) +
  geom_errorbar(position=position_dodge(width=.25), width=0) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","grey")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.85),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure", shape="News Exposure")

>>>>

fit_s2_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s2_reg,
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.99),
  seed = 46179,
  file = "../local/fit_s2_vaccIntent.rds"
)

@@

  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption, escape = F, format="latex") %>% 
    kableExtra::kable_classic(full_width=F)
}

fit_s2_vaccIntent %>% 
  make_table_df() %>% 
  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
  mutate(
    Term = case_when(
      grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta_{",
                                                 gsub("(diseaseRisk|post)", "", Term),
                                                 "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(diseaseRisk|post)","", Term)
    )
  ) %>% 
  make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")

@@

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  # group_by(scale) %>% 
  # mutate(post = post/sd(post), pre = pre/sd(pre)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

fit_s3_vaccIntent %>% 
  make_table_df() %>% 
  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
  mutate(
    Term = case_when(
      grepl("(intervention|post)", Term) ~ paste0("$\\beta_{",
                                                 gsub("(intervention|phase)", "", Term),
                                                 "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions combining data from Experiments 3a and 3b.")
```

@@

fit_s3a_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="A"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.99),
  seed = 69568,
  file = "../local/fit_s3a_vaccIntent.rds"
)

fit_s3b_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="B"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.99),
  seed = 69568,
  file = "../local/fit_s3b_vaccIntent.rds"
)

fit_s3a_vaccIntent %>% 
  make_table_df() %>% 
  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
  mutate(
    Term = case_when(
      grepl("(intervention|post)", Term) ~ paste0("$\\beta_{",
                                                 gsub("(intervention|phase)", "", Term),
                                                 "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3a.")

fit_s3b_vaccIntent %>% 
  make_table_df() %>% 
  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
  mutate(
    Term = case_when(
      grepl("(intervention|post)", Term) ~ paste0("$\\beta_{",
                                                 gsub("(intervention|phase)", "", Term),
                                                 "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3b.")
```

@@

```{r echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the toxins intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.15),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

fit_s4_vaccIntent <- brm(
  response ~ phase*vacc_news + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s4_reg %>% filter(scale=="vaccIntent"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.99),
  seed = 40725,
  file = "../local/fit_s4_vaccIntent.rds"
)

fit_s4_vaccIntent %>% 
make_table_df() %>% 
  rename(`$CI_{2.5\\%}$` = `l-95% CI`,`$CI_{97.5\\%}$` = `u-95% CI`) %>% 
  mutate(
    Term = case_when(
      grepl("(vacc_news|post)", Term) ~ paste0("$\\beta_{",
                                                 gsub("(posttest)", "", Term),
                                                 "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(posttest)","", Term)
    ),
    Term = gsub("vacc_news", "awareness", Term)
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
```

@@

```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4. Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York. Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak. In both plots, error bars represent 95\\% confidence intervals."}
s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(posttest = rescale_beta(posttest, -3, 3), pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll95, ymax=ul95, color=vacc_news, shape=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2) +
  geom_errorbar(position=position_dodge(width=.25), width=0) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","grey")) +
  # scale_shape_manual(values=c(17,16)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.85),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure", shape="News Exposure")
